Appendix B

### 2021-11-03 manuscript.Rmd
added references for Survey and related questionnaires

+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+

@@

+=================================================+============================+===========================================================================================+================+=============+

@@

+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                           |                |             |
+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+

@@

+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new] \|     | Eight-question survey to assess the presence and severity of photosensitivity symptoms \| | All items \|   |             |
+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
|                                                 |                            |                                                                                           |                |             |
+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+

@@

Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>). Participants were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].

@@

-   Sleep disturbance and sleep-related impairment [CITE]
-   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [CITE]
-   Meal timing & caffeine consumption [CITE]
-   Light sensitivity (photophobia vs. photophilia) [CITE]
-   Self-reported pubertal stage (only if younger than 18 years old) [CITE]

>>>>

+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+

@@

+===================================================================+==========================+==============================================================================================================================================================+======================================+=============+

@@

+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
| Assessment of Sleep Environment                                   | [@Olivier.2016]          | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+

@@

+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | [@Xie.2021]              | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25. and 29. |             |
+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
| Photosensitivity Assessment Questionnaire (PAQ)                   | [@Wu.2017]               | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+

@@

Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>). Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].

@@

-   Sleep disturbance and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011]
-   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
-   Sleep environment [@Olivier.2016]
-   Meal timing & caffeine consumption [custom items]
-   Light sensitivity (photophobia vs. photophilia) [@Wu.2017]
-   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
